Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-04-12 paper/AlignedIsotropicGW.tex
Updating chi text.

Figure \ref{fig:O1-posteriors} shows an approximation to the posterior
inferred on $\chieff$ for the three likely \ac{GW} detections
GW150914, GW151226 and LVT151012 from Advanced LIGO's first observing
run (O1) \citep{O1-BBH}.  Because samples drawn from the posterior on
$\chieff$ are not publicly released at this time, we have approximated
the posterior as a Gaussian distribution with the same mean and 90\%
credible interval as quoted in \citet{O1-BBH}.  Since all three
mergers involve black holes of comparable masses, there is essentially
no posterior support for both black holes' $\chi \gtrsim 0.5$, in
contrast to the majority of the electromagnetically-detected
stellar-mass black hole population (see Section \ref{sec:discussion}).
The analysis here is relatively insensitive to the precise details of
the posterior distributions; other conclusions are more sensitive.  In
particular, our Gaussian approximation does permit $\chieff = 0$ for
GW151226 while the true posterior rules this out at high confidence
\citep{2016PhRvL.116x1103A,O1-BBH}.

>>>>

Figure \ref{fig:O1-posteriors} shows an approximation to the posterior
inferred on $\chieff$ for the three likely \ac{GW} detections
GW150914, GW151226 and LVT151012 from Advanced LIGO's first observing
run (O1) \citep{O1-BBH}.  Because samples drawn from the posterior on
$\chieff$ are not publicly released at this time, we have approximated
the posterior as a Gaussian distribution with the same mean and 90\%
credible interval as quoted in \citet{O1-BBH}.  \ilya{None of the $\chieff$ posteriors are consistent with two black holes with large aligned spins, $\chi_{1,2} \gtrsim 0.5$; this contrasts with the large spins inferred for the majority of black holes in X-ray binaries  (see Section \ref{sec:discussion}).}
\sout{Since all three
mergers involve black holes of comparable masses, there is essentially
no posterior support for both black holes' $\chi \gtrsim 0.5$, in
contrast to the majority of the electromagnetically-detected
stellar-mass black hole population (see Section \ref{sec:discussion}).}
The analysis here is relatively insensitive to the precise details of
the posterior distributions; other conclusions are more sensitive.  In
particular, our Gaussian approximation does permit $\chieff = 0$ for
GW151226 while the true posterior rules this out at high confidence
\citep{2016PhRvL.116x1103A,O1-BBH}.
